Development of a 3D display

### 2016-05-13 paper.tex
%s/\\item/\t\\item/g
Finished chapter 2

In order for the production to be as cheap as possible as well as to minimise the rotating mass, I tried
to make the boards as small as possible. Ultimately, I managed to bring the size down to 
\SI{73}{\milli\meter} by \SI{21}{\milli\meter}

>>>>

In order for the production to be as cheap as possible as well as to minimise the rotating mass, I 
tried to make the boards as small as possible. Ultimately, I managed to bring the size down to 
\SI{73}{\milli\meter} by \SI{21}{\milli\meter}.

In order to achieve this, but also to avoid large gaps between the pixels, I placed the LEDs as 
close as possible to each other. The datasheet claims a width of \SI{2.8 +- 0.2}{\milli\meter}, 
so I decided to place the LEDs at \SI{3}{\milli\metre} increments. On a grid of \SI{12.5}{mil}, 
the next larger distance is \SI{125}{mil}, which is equal to \SI{3.175}{mm}.

The connections to the cathodes of the red LED needs to pass by the other two cathodes, since 
they're located on the lower side of the LED package. Because the LEDs are so close to each other, 
the only option was to use the lower copper layer. The only place to go back to the upper copper 
layer was right beneath the driver chips.

Initially, I had placed the capacitors right above the ICs. However, I could save a small bit of
vertical board size by placing them at an offset to the right. That way I could push them down 
until where the pins begin, which is a bit further down than the edge of the chip itself.

\subsection{Thermal Considerations}

A positive side effect of placing some vias beneath the chip is their thermal conductivity. That
way, the chips' waste heat can be dissipated more effectively. The maximum power output of the 
chips --- when all the attached LEDs are turned on --- is as follows:

\begin{ownmath}
\textrm{P\textsubscript{MAX}} = (\SI{5}{\volt} - \textrm{V\textsubscript{F}}) * 
\SI{20.6}{\milli\ampere\per output} * \SI{16}{outputs} = \SI{867.9}{\milli\watt}
\end{ownmath}

V\textsubscript{F} is different depending on the colour of the LED, so I just used the average
value, which is \SI{2.633}{\volt}. The actual values are \SI{1.9}{\volt} for red and \SI{3}{\volt}
for green and blue.

A power output of almost a watt is not to be underestimated, and tests have shown that that the
boards do get quite hot when operated at full power. In reality, however, the situation is much
less severe because the LEDs are typically turned on only during a fraction of the rotation.
Furthermore, the quick rotation results in excellent air circulation, which aids the dissipation
of heat.
